### 2011-08-24 pretextual.tex
quotation no Newton modified:   pretextual.tex

	\begin{epigrafebot}
		{Do not worry about your difficulties in Mathematics. \\ I can assure you mine are still greater.} %frase
		{Albert Einstein (1879 - 1955)} %referência
	\end{epigrafebot}

>>>>

	\begin{epigrafebot}
		{If I have seen further, it is by standing on the shoulders of giants.} %frase
		{Sir Isaac Newton (1642 - 1727)} %referência
	\end{epigrafebot}
